The Name of the Title Is Hope

### 2024-05-09 paper/paper.tex
Text

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Abstract goes here
\end{abstract}

@@

\section{How to pitch this paper and What is the unique selling point of our work?}
Our Coq formalisation can be used at front-end to generate Web Assembly code and 
Rust code at the back-end. Contrary to the existing work, our formalisation
does not write the same code twice. But sigma protocols are arcane and has 
been formalised couple of times before so why another formalisation?
None of the formalisation has been able to extract the code to executable code 
and one that was able to do so did not reason about probabilities in an intuitive way.
Moreover, that work was just geared towards verifying a transcript rather than
constructing it. Also, recently ZKP community started a movement to 
formalise the Sigma protocols. We also demonstrates the 
applicability of our formalisation by encoding Helios cryptographic protocols
in our formalisation.

\section{Introduction}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), Sigma protocols remain a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
Moreover, recently ZKP community started a movement to standardise
the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
they possess some knowledge without revealing anything else about the knowledge itself.  
More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems, 
at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
Web Assembly and Rust.

There are numerous implementations of Sigma protocols in various languages, 
e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
However, there are two main issues with these implementations: (i)  
the same code is written twice 
once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java),
especially in privacy-preserving voting systems such as Helios, SwissPost, and 
(ii) none of these implementations offer any formal guarantees about the correctness of the code.
Given the importance of Sigma protocols in privacy-preserving voting systems,
it has been formalised couple of times before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
pen-and-paper proofs of Sigma protocols into theorem provers, and not extracting an executable code.
On the other hand, \cite{10.1145/3319535.3354247} exatract an OCaml code from Coq 
formalisation but it is mostly geared towards verifying an Helios election transcript, 
rather than constructing the primitives to conduct an election. Moreover, 
it lacks many primitives and does not reason about probabilities in an intuitive way.

In this paper, we present a formal verification of Sigma protocols in the Coq proof assistant that 
can be used to generate Web Assembly code at the front-end and Rust code at the back-end. 
We use our formalisation to model the cryptographic protocols implemented in Helios voting systems.

@@

Zero-knowledge proofs are a class of cryptographic protocols that allow a
prover to convince a verifier that a statement is true without revealing 
any information about the statement itself. 
Zero-knowledge proofs are possible for all problems in the $NP$ complexity class. 
$NP$ includes problems where a proof of membership can be efficiently 
verified in polynomial time. In NP, a witness (denoted as $w$) is a 
polynomial-length piece of evidence that allows quick
verification (in polynomial time) that a given statement $s$ 
belongs to the language. This verification process can be represented 
using a binary relation $R$ between the set of statements (S) and the 
set of witnesses ($W$), where $(s, w) \in R$ if the witness $w$ 
demonstrates that the statement $s$ is in the language.

Sigma protocols are a class of cryptographic protocols that are used to prove the 
knowledge of a witness for a given statement.

They are used in various cryptographic 
applications such as identification, authentication, and zero-knowledge proofs. 
The security of these protocols is based on the hardness of certain mathematical 
problems such as the discrete logarithm problem. Amongst sigma protocols, 
one of the most well-known protocols is the Schnorr protocol. In this 
paper, we present a formal verification of the Schnorr protocol in the
Coq proof assistant.

\section{Sigma Protocols}

  Explain here the definition of Sigma Protocols and the Schnorr protocol.

@@

\section{Formal Verification of Sigma Protocols}

@@

\section{Case Studies}
  We use our formalisation to model the Cryptographic protocols implemented in 
  Helios voting systems.

@@

\section{Conclusion, Future Work, and Limitations}

>>>>

%% get rid of this for the final version
\usepackage{todonotes}
\usepackage{listingsutf8}
\setlength {\marginparwidth }{2cm} %This is for todod
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{cryptocode}
\usepackage{lstcoq}
\usepackage[utf8]{inputenc}
%% End of get rid of this for the final version

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZKSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in prominent e-voting systems such as 
  Helios, Belenois, and SwissPost \textbf{More examples}. However, 
  the existing implementations of sigma protocol have two 
  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
  and (ii) none of these implementations offer any security guarantees. 
  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant. 
  We prove that our implementation is (special) sound, complete, and 
  (honest verifier) zero-knowledge. Moreover, 
  we compile our Coq formalisation to WebAssembly and Rust, and 
  thereby solve the problem of writing the same code twice. 
  We demonstrate the applicability of our
  formalisation by encoding the cryptographic protocols implemented in 
  Helios, Belenois, and SwissPost voting systems. 
  Our long terms goal is to provide a verified cryptographic library that can be 
  readily used in privacy-preserving voting systems.

\end{abstract}

@@

\section{How to pitch this paper and What is the unique selling point of our work?}
Our Coq formalisation can be used at front-end (WebAssembly code) and 
back-end (Rust). Contrary to the existing work, our formalisation
does not write the same code twice. But sigma protocol is arcane and has 
been formalised couple of times before so why another formalisation?
None of the formalisation has been able to extract the code to executable code 
and one that was able to do so did not reason about probabilities in an intuitive way.
Moreover, that work was just geared towards verifying a transcript rather than
constructing it. Also, recently ZKP community started a movement to 
formalise the sigma protocols. We also demonstrates the 
applicability of our formalisation by encoding Helios cryptographic protocols
in our formalisation.

@@

\section{Introduction}

\textbf{Emphasise how Sigma protocol is still used in elections to a public office}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), sigma protocol remains a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
Belenois --used in French elections for overseas 
voters\footnote{VVFE, used in French elections, is a derivative of (part of) Belenios and 
inherited all the zero-knowledge proofs from Belenois.}-- \cite{cortier2023french}, and 
SwissPost --used in Swiss elections for overseas voters-- voting 
systems \cite{10.1007/978-3-031-15911-4_4} (\textbf{Look for more examples}). 
Moreover, recently zero-knowledge proof community started a movement to standardise
the sigma protocol \cite{ZKProof}.
One of the main reasons for its popularity in privacy-preserving voting systems is its simplicity and 
well-understood security.

%\textbf{Introduce here that sigma protocol is efficient and simple and all other details about sigma protocol.} 
Zero-knowledge proofs are possible for all problems in the $NP$ complexity class, which 
includes problems where a proof of membership can be efficiently verified in polynomial time.
Sigma protocol is a simple and efficient zero-knowledge proof where the verifier  is assumed to be honest. 
More formally, for a given $NP$-relation $R$ and a statement $x$, a sigma protocol allows a prover 
$P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
that ($x$, $w$) $\in$ $R$. To accomplish this, $P$ and $V$ engage in a three move 
interactive protocol (shown below). At the end of the protocol $V$ either accepts or rejects the proofs.
Like any other proof system, sigma protocols also has completness and (special) soundness; moreover,  
it also has an additional property (special honest-verifier) zero-knowledgeness.

\textbf{Draw a move }

\definition{Completeness}
when $P$ and $V$ follow the protocol, then $V$ always accepts. In other words, 
if $P$ knows $w$ for $x$ then it would successfully construct a triple 
(a; c; r) that always passes the verification equation, i.e., $V$ accepts.

\definition{Special soundness}
there exists a probabilistic polynomial time extractor $E$ which given 
two accepting transcripts (a; c; r) and (a; c', r') for $x$, then 
it can extract a witness $w$ such that $(x, w) \in R$. In other words, 
if $P$ does not know $w$ for $x$ then it cannot create a proof 
(a; c; r) that will passes the verification check.

\definition{Special honest-verifier zero-knowledge proof}
there exists a probabilistic polynomial-time simulator S that for  
any $v$ in $L_R$ and $c \in C$, $S$ generates conversations 
(a,c,r) with the same probability as honest conversations between 
$P$ and $V$ using $w$ satisfying $(v,w) \in R$.

Sigma protocol was first defined by Ronald Cramer \cite{cramer1996modular} 
and the first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, 
Belenois, SwissPost, etc. Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems, 
at least in the existing voting systems. Ideally, given the abstraction of 
our formlisation (vector space) we could have abstracted the 
sigma protocol and their composition in a generic way \cite{10.1007/978-3-642-02384-2_17},
but we decided to focus on the Schnorr protocol and its composition to ensure nice and familiar APIs 
for e-voting in Web Assembly and Rust.

There are numerous implementations of sigma protocol in various languages, 
e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
However, there are two main issues with these implementations: (i)  
the same code is written twice 
once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java),
especially in privacy-preserving voting systems such as Helios, SwissPost, and 
(ii) none of these implementations offer any formal guarantees about the correctness of the code.
Given the importance of sigma protocols in privacy-preserving voting systems,
it has been formalised before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
pen-and-paper proofs of sigma protocol into theorem provers and not extracting an executable code.
On the other hand, \cite{10.1145/3319535.3354247} exatract an OCaml code from Coq 
formalisation but it is mostly geared towards verifying an Helios election transcript, 
rather than constructing the primitives to conduct an election. Moreover, 
it lacks many primitives and does not reason about probabilities in an intuitive way.

\subsection{Contribution}
In this paper, we present a certified implementation sigma protocol and its composition 
in the Coq proof assistant.

Moreover, we extract WebAssembly and Rust code from our 
certified implementation. 
We use our formalisation to model the cryptographic protocols implemented in Helios, 
Belenois, and SwissPost voting systems. To the best of our knowledge, this is the first
formal verification of Sigma protocol that can be used at the front-end (WebAssembly code) and
back-end (Rust code).

\section{Coq formalisation}

  We briefly explain the Schnorr protocol, which is very similar to 
  the one we explained in the introduction section.
  Given some public input $(G, g, q, h)$ where $G$
  is a cyclic group of prime order $q$, and $g$ and $h$ are two 
  generators of the group $G$, the prover claims that they know a
  witness $w$ for the statement $h = g^w$; the existence of such
  a $w$ is immediate because $g$ generates the group. However,
  does the prover know the witness $w$? In order to convince the
  verifier, the prover and the verifier do the following:
  \begin{itemize}
    \item the prover picks a random number $u$, computes $c = g^u$,
    and sends $c$ to the verifier.
    \item the verifier picks a random challenge $e$ and sends it to
    the prover
    \item the prover computes $t = u + e * w$ and sends $t$ to the
    verifier
  \end{itemize}

The verifier accepts if $g^t = c * h^e$, otherwise rejects. 
We model the Schnorr protocol in Coq as follows:

\begin{lstlisting}[language=Coq]
  Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
    @sigma_proto 1 1 1 :=  ([g^u]; [c]; [u + c * x]).
\end{lstlisting}

 where $F$ is the underlying field, $G$ is the underlying group,
 $+ : F \rightarrow F \rightarrow F$ is field addition,
 $* : F \rightarrow F \rightarrow F$ is field multiplication, and
 $\textasciicircum : G \rightarrow F \rightarrow G$ scalor multiplication. 
 We emphasise that we work in abstract setting of \textbf{vector space} to 
 make the implementation as general as possible. Recall that a vector space consists of a set of 
 vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
 two operations: vector addition and scalar multiplication.

\begin{itemize}
    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
\end{itemize}

These operations must satisfy the following properties for all vectors \(\mathbf{u}, \mathbf{v}, \mathbf{w} \in V\) and all scalars \(c, d \in F\):
(i) \textbf{Closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{Commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
(iii)  \textbf{Associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
(iv) \textbf{Existence of zero vector:} There exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
(v) \textbf{Existence of additive inverse:} For each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
(vi) \textbf{Closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
(vii) \textbf{Distributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
and (viii) \textbf{Compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
In our setting we instantiate the set of vectors with group $G$ and field with $F$. Moreover, our notation for scalar multiplication 
is $\textasciicircum$ because it represents, when instantiated concretely, exponentiation function. Finally, 
we define two more functions

\begin{lstlisting}[language=Coq]
(* Fake transcript (without the witness x) *)
Definition schnorr_simulator (g h : G) (u c : F) : 
@sigma_proto 1 1 1 := ([gop (g^u) (h^(opp c))]; [c]; [u]).

(* 
  This function checks if a conversation (a; c; r) 
  is accepting or not. It checks if g^r = a * h^c
*)
Definition accepting_conversation 
  (g h : G) (v : @sigma_proto 1 1 1) : bool :=
  match v with
  | (a; c; r) =>  
    match Gdec (g^(hd r)) (gop (hd a) (h^(hd c))) with 
    | left _ => true
    | right _ => false 
    end
  end.

(* Distribution that involves the secret x *)
Definition schnorr_distribution  (lf : list F) 
  (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
  dist sigma_proto :=
  (* draw u from a random distribution *)
  u <- (uniform_with_replacement lf Hlfn) ;;
  Ret (schnorr_protocol x g u c).

(* without secret x *)
Definition simulator_distribution (lf : list F) 
  (Hlfn : lf <> List.nil) (g h : G) (c : F) : 
  dist sigma_proto :=
  (* draw u from a random distribution *)
  u <- (uniform_with_replacement lf Hlfn) ;;
  Ret (schnorr_simulator g h u c).
\end{lstlisting}

Finally we establish the completeness, special soundness, 
and special honest-verifier zero-knowledge proof. 
\begin{lstlisting}[language=Coq]
Lemma schnorr_completeness : 
  forall (r c : F) (a : t G 1) (c r : t F 1),
  (a; c; r) = (schnorr_protocol x g r c) ->
  accepting_conversation g h (a; c; r) = true.
Proof. (* proof terms omitted *) Qed.

Lemma simulator_completeness : 
    forall (r c : F) (a : t G 1) (c r : t F 1),
    (a; c; r) = (schnorr_simulator g h r c) ->
    accepting_conversation g h (a; c; r) = true.
  Proof using -(x R). (* proof terms omitted *) Qed.

Lemma special_soundness: 
  forall (a : G) (ca ra cb rb : F), ca <> cb ->
  accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
  accepting_conversation g h ([a]; [cb]; [rb]) = true ->
  (* then we can find a witness y such that g^y = h *)
  exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
Proof using -(x R). (* proof terms omitted *) Qed.

(* it's identical, i.e., information theoretic zero-knowledge proof *)
(* Under the hood, it is modelled as a list and looks like:
    [((a; c; r), prob); ((a; c; r), prob) ......].
  We map accepting_conversation to crunch the first pair, 
  (a, c, r), and produce boolean a value (true), 
  and then we show that these two distribution are 
  identical 
*)
Lemma special_honest_verifier_zkp : 
  forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
  List.map (fun '(a, p) => (accepting_conversation g h a, p))
    (@schnorr_distribution lf Hlfn x g c) = 
  List.map (fun '(a, p) => (accepting_conversation g h a, p))
    (@simulator_distribution lf Hlfn g h c).
Proof. (* proof terms omitted *) Qed.

\end{lstlisting}

In our library, we have encoded Parallel composition, 
AND composition, OR composition, EQ composition, and 
NEQ composition. Below we explain the OR composition
beause it is more involved than the rest.

  However, we would like 
  to emphasise that we worked in a vector-space, rather 
  than concrete numbers. Working in (abstract) vector-space makes our system 
  amenable to be instantiated by any group and field 
  (Elliptic curve vs Concrete Nubmers). \textbf{Currently, 
  our library comes with concrete nubmers but it can easily be 
  instantiated with Elliptic curve cryptography}

  \textbf{Coq code of Schnorr goes here}

  The reader can see that we have used vector space. Now 
  we establish completeness, (special) soundness, and zero-knowledge 
  proof of knowledge (ZkPOK).

  \textbf{Coq code soundness, completeness, zkp goes here}

  The proof of completeness and soundness are fairly straightforward but 
  zero-knowledge proof of knowledge requires probabilistic reasoning.

  \textbf{Coq code goes here}

  In our library, we have encoded Parallel composition, 
  And composition, Or composition, EQ composition, and 
  NEQ composition. Below we explain the OR composition
  beause it is more involved than the rest.

  \textbf{OR composition and Coq code}

@@

  \subsection{Uniform Distribution}
  To reason about probabilistic distribution, 
  we have encoded probability as list.

  \subsection{Fiat-Shamir Transform}
 We have formalised the interactive version of sigma protocol. However,
 interaction is not convenient and therefore
 we use Fiat-Shamir transform to make it non-interactive. We use SHA256 
 to turn the interaction to non-interaction but in order to 
 make it a self-contained library and 
 avoid relying on any external library at the front-end (WebAssembly)
 we have encoded the SHA256 in the Coq theorem prover, with usual correctness 
 properties.

 \subsection{Efficient Modular Arithmetic}
  In order to call the functions from our formalisation, 
  a user need to instantiate

@@

\section{Case Studies/Experiment}
  We use our formalisation to model the Cryptographic protocols implemented in 
  Helios voting systems. Compare it with state-of-the-art 
  crypto library.

@@

\section{Conclusion, Future Work, and Limitations}
  In this paper, we present a certified implementation 
  that can be readily used by voting community and 
  we demonstrated the usefulness by encoding Helios, 
  Belenois, and SwissPost using our primitives. 
  Moreover, our formalisation extracts to WebAssembly and 
  Rust without duplicate efforts.

\section{DECRA}
The aim of this project is to investigate the applicability of 
zero-knowledge succinct argument of knowledge (ZKSNARK) 
to reduce the data breaches.
